Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/fig-motivation.tex
x

\begin{figure*}
\begin{tabular}{@{}llll @{}}
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
  Memory corruption\footnote{We classified the following vulnerabilities as memory corruption
    attacks based on their description: 2013-5660, - 0742, -0138, 2012-4987, -1163,-1162, 2011-2265,
    2010-4535, -1657, -1336, -1218} & 2013-5660 & Buffer overflow & 11\\
  Parser ambiguities & 2013-1462 & Multiple virus scanners interpret ZIP files incorrectly.& 4\\
  Semantic misunderstanding & 2014-2319 & Compressor uses weak cryptography, even if the user
  selects AES & 1\\
  \multicolumn{3}{l}{\bf Total vulnerabilities related to .zip processing }& \bf 16  \\  
  Mishandling archive contents &  2012-4389 & 
\begin{minipage}{7cm}
A web application overwrites .htaccess files and
  executable files by extracting uploaded .ZIP files to a publicly accessible folder  
\end{minipage}& 25\\
   Unrelated to .zip &2011-3371& Vulnerability leaking postal Zip codes & 42\\
  \multicolumn{3}{l}{\bf Total vulnerabilities} & \bf 83\\

\end{tabular}
\caption{Classification of known vulnerabilities in the CVE database between 2010 and 2014 related to the search term ``ZIP''}
\label{fig:motivation} 
\end{figure*}

>>>>

\begin{figure*}
\centering
\begin{tabular}{llll}
\toprule
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
\midrule
  Memory corruption\footnote{We classified the following vulnerabilities as memory corruption
    attacks based on their description: 2013-5660, - 0742, -0138, 2012-4987, -1163,-1162, 2011-2265,
    2010-4535, -1657, -1336, -1218} & 2013-5660 & Buffer overflow & 11\\
  Parser ambiguities & 2013-1462 & Multiple virus scanners interpret ZIP files incorrectly.& 4\\
  Semantic misunderstanding & 2014-2319 & Weak cryptography used even if user selects AES & 1\\
  \multicolumn{3}{l}{\bf Total vulnerabilities related to .zip processing }& \bf 16  \\
\bottomrule

\end{tabular}
\caption{Classification of known vulnerabilities in the CVE database
between 2010 and 2014 related to the search term ``ZIP'' and involving
the ZIP file format.}
\label{fig:motivation} 
\end{figure*}

### 2014-05-02 paper/osdi14/motivation.tex
x

To motivate the need for Nail, this section presents a case study of
vulnerabilities due to ad-hoc input parsing and output generation.

\paragraph{Parsing bugs} Two recent high profile security vulnerabilities in mobile operating systems are due to improper
input recognition, without using any memory corruption. In both cases, when the vulnerabilities were
fixed, a similar flaw was exposed immediately afterwards, showing the need for a different approach
to input handling that eliminates those vulnerabilities by design.

@@

Implementations of the X.509 format for SSL certificates were also shown to parse various ASN.1
structures, such as length fields, strings containing invalid characters and repeated fields with
conflicting values different ~\cite{DBLP:conf/fc/KaminskyPS10}. For example, certificates could be
crafted where the X.509 parsers used certificate authorities and web browsers disagree on the
subject of the certificate, allowing an attacker to get certificates for domains they do not control.

@@

@@

The fourth vulnerability (CVE-\XXX) is the Android master key bug mentioned above, which results
from one parser interpreting a size field as an unsigned integer, another interpreting the same
field as a signed integer.

>>>>

To motivate the need for Nail, this section presents a case study of
vulnerabilities due to ad-hoc input parsing and output generation.
Broadly speaking, parsing vulnerabilities can lead to two kinds of
problems---memory corruption and logic errors---and as we show, both
are prevalent in software and lead to significant security problems.

\paragraph{Widely exploited parsing errors.}

Three recent high profile security vulnerabilities are due to logic
errors in input processing.  In all cases, when the vulnerabilities were
fixed, a similar flaw was exposed immediately afterwards, showing the
need for a different approach to input handling that eliminates those
vulnerabilities by design.

@@

Implementations of the X.509 format for SSL certificates were also shown to parse various ASN.1
structures, such as length fields, strings containing invalid characters and repeated fields with
conflicting values different~\cite{DBLP:conf/fc/KaminskyPS10}. For example, certificates could be
crafted where the X.509 parsers used certificate authorities and web browsers disagree on the
subject of the certificate, allowing an attacker to get certificates for domains they do not control.

@@

\paragraph{Case study: ZIP file handling.}

@@
